### 2014-10-24 Projects/NFRL_Emissions/Report/ECS_Testing.tex
ECS: minor update to report

Overall, three different fuel packages were used to test the system's cabilitity to independently handle elevated temperatures, scrub acid gas, and trap particulates. Table ~\ref{tab:fires} shows the fire tests to be conducted. Two tests were conducted with each fuel package to ensure that each train within the new ECS was independently tested. For the gas burner tests, three tests were conducted; one for each of the the trains and one with both trains running together to test heat release rates larger than 5~MW.

\begin{table}
\centering
\caption{Design fires for ECS commissioning tests}
\label{tab:fires}
\begin{tabular}{lccl}
\toprule[1.5pt]
Fuel & Peak HRR (MW) & Burn Time (min) & Test Goal  \\
\midrule
Natural Gas   & 2-8             & 60            & Temperature  \\
Wood w/ PVC   & $\approx$ 1.5-2 & $\approx$ 50  & Acid Gases \\
Group A Comm. & $\approx$ 3     & $\approx$ 20  & Soot \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

The burning rate of wood cribs is found from experiments performed by Madrzykowski and Stroup \cite{Madrzykowski1998} and Bryner and Mulholland \cite{Bryner1991}. The steady burning rate averaged over the peak 50 \% of burning is 0.03 kg/s. If an entire 34 kg crib burned at this rate, the burn would last approximately 19 minutes. If we estimate that 50 \% of the mass burns at 0.03 kg/s and the remaining 50 \% burns at $1/3$ the burning rate, 0.01 kg/s, then a crib burn would take approximately 40 minutes. The bottom three cribs in Fig.~(\ref{fig:test_crib}) are all ignited at nominally the same time. Therefore we can assume that all three will burn for about 40 minutes. If we assume an ignition delay of 5 minutes, a conservative estimate for total burn time is 45 minutes. This falls into the range of experimental burn durations from \cite{Bryner1991} of 40 to 65 minutes.

>>>>

Overall, three different fuel packages were used to test the system's cabilitity to independently handle elevated temperatures, scrub acid gas, and trap particulates. Table ~\ref{tab:fires} shows the fire tests to be conducted. Two tests were conducted with each fuel package to ensure that each train within the ECS was independently tested. For the gas burner tests, three tests were conducted; one for each train and one utilizing both trains to test heat release rates larger than 5~MW.

\begin{table}[!h]
\centering
\caption{Design fires for ECS commissioning tests}
\label{tab:fires}
\begin{tabular}{lccl}
\toprule[1.5pt]
Fuel & Peak HRR (MW) & Burn Time (min) & Test Goal  \\
\midrule
Natural Gas   & 2-8             & 60            & Temperature  \\
Wood w/ PVC   & $\approx$ 1.5-2 & $\approx$ 50  & Acid Gases \\
Group A Comm. & $\approx$ 3     & $\approx$ 20  & Soot \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

The burning rate of wood cribs was found from experiments performed by Madrzykowski and Stroup \cite{Madrzykowski1998} and Bryner and Mulholland \cite{Bryner1991}. The steady burning rate averaged over the peak 50~\% of burning is 0.03~kg/s. If an entire 34~kg crib burned at this rate, the burn would last approximately 19 minutes. If we estimate that 50 \% of the mass burns at 0.03 kg/s and the remaining 50 \% burns at $1/3$ the burning rate, 0.01 kg/s, then a crib burn would take approximately 40 minutes. The bottom three cribs in Fig.~(\ref{fig:test_crib}) are all ignited at nominally the same time. Therefore we can assume that all three will burn for about 40 minutes. If we assume an ignition delay of 5 minutes, a conservative estimate for total burn time is 45 minutes. This falls into the range of experimental burn durations from \cite{Bryner1991} of 40 to 65 minutes.
